### 2009-12-04 docs/marcello-dissertation/thesis/chapter2-state-of-the-art.tex
Fixing typos on chapter 2, since the writing was very incorrect :)
git-svn-id: svn://localhost/netbeams/branches/marcello/persistence@669 559edde2-a4d4-44e0-96fc-4035e40d7396

The property of coverage on a sensor network is defined by
\cite{sn-intro01} as the physical space ``visible" to the sensors devices, which
is also directly related to the purpose of the network, its size in terms of
the number of nodes deployed and the sensor network lifetime. Therefore,
sensors are deployed in sparse or dense manners, according to the
specification of what needs to be covered by the sensor devices. Furthermore,
considering that some types of sensor devices are very likely to regular
hardware failures, \cite{sn-intro2} described sensor network examples with 
redundant nodes that provide better data coverage and levels of coverage.
Finally, the coverage of sensor devices also influence on the connectivity
property of the sensor nodes. In order communicate with redundant nodes, a
physical connection must be available at all times. On the other hand, lower
level of coverage is is related sporadic communication among the sensor nodes.

@@

Depending on the application of the collected sensor data, the location in
which the data was collected may be needed. For example, \cite{sn-geo-metadata}
shows the geographic location of the collected data is critical to identify
the locations of the events of the sensor device \cite{sn-ex02}. Similarly,
the position of any event captured in a black-box of an aircraft carries is
also used as metadata for the event. For this reason, engineers can open a
real-world explanation regarding my family.

All in all, Data Provenance enriches the value of the collected sensor,
describing its identity creation, taking into account the specific location
where the data was deployed. Such application ca be seen by having the problems
and solutions Information Fusion \cite{sn-info-fusion}.

>>>>

The property of coverage on a sensor network is defined by
\cite{sn-intro01} as the physical space ``visible" to the sensors devices, which
is also directly related to the purpose of the network, its size in terms of
the number of nodes deployed and the sensor network lifetime. Therefore,
sensors are deployed in sparse or dense manners, according to the
specification of what needs to be covered by the sensor devices. Furthermore,
considering that some types of sensor devices are very likely to regular
hardware failures, \cite{sn-intro02} described sensor network examples with 
redundant nodes that provide better data coverage and levels of coverage.
Finally, the coverage of sensor devices also influence on the connectivity
property of the sensor nodes. In order communicate with redundant nodes, a
physical connection must be available at all times. On the other hand, lower
level of coverage is is related sporadic communication among the sensor nodes.

@@

Depending on the application of the collected sensor data, the location in
which the data was collected may be needed. For example, \cite{sn-geo-metadata}
shows the geographic location of the collected data is critical to identify
the locations of the events of the sensor device \cite{sn-ex02}. Similarly,
the position of any event captured by a black-box of an aircraft carries 
metadata for the event. Examples of this are the metadata event =
``high-pressure" of 1304, at the altitude of 1,500 feet above the ocean on GPS
coordinates of latitude 13.445 and longitude -23,003. This example clearly
gives necessary identification of where the event of high-pressure occurred.

All in all, Data Provenance enriches the value of the collected data from
sensor devices by describing its identity creation, time of creation and
specific location where the observation occurred. It is important to note,
however, that those type of data do not necessarily need to be on the data
model used, but the specifications of the use of the data determines which
ones are needed. Finally, collected data that are provenance-aware has a direct
use on technologies called Information Fusion \cite{sn-info-fusion}, which aims
at using data from different sensor devices.
